Unified Linear Speedup Analyses of Communication-Efficient Stochastic FedAvg and Nesterov FedAvg

### 2021-07-11 source/main.tex
Add bio

\begin{comment}

\begin{IEEEbiography}{Zhaonan Qu}
Biography text here.
\end{IEEEbiography}

@@

@@

\end{comment}

>>>>

% \begin{comment}

\newpage
\begin{IEEEbiography}{Zhaonan Qu}
Biography text here.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaojian.png}}]{Zhaojian Li}
Dr. Zhaojian Li is an assistant Professor in the Department of Mechanical Engineering at Michigan State University. His main research interests include Robotics and Autonomous Vehicles, Intelligent Transportation System, Reinforcement Learning, Vehicle Dynamics, and Optimal Control.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhengyuan.png}}]{Zhengyuan Zhou}
Dr. Zhengyuan Zhou is an assistant professor in the Department of Technology, Operations, and Statistics at Stern School of Business, New York University. Before joining NYU Stern, he obtained Ph.D. degree in the Information System Laboratory in Department of Electrical Engineering at Stanford University. 
\end{IEEEbiography}

% \end{comment}
